---
title: "Data607 - Week 3 Assignment"
author: "Anthony Josue Roman"
date: "2024-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
```

This assignment will use the following packages:

```{r eval=FALSE}
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
```

## Question 1

Utilizing the 173 majors listed on [fivethirtyeight](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/). The link to the dataset is within this github link [here](https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv), which will also be uploaded onto my github [page](https://github.com/spacerome/Data607_Assignment_3). Using the following data from the csv file the following code will identify the majors that contain either "Data" or "Statistics".

```{r echo=TRUE}
a <- getwd() # Just to set directory
setwd(a)
majors <- read.csv("majors-list.csv")

head(majors)

grep("DATA|STATISTICS", majors$Major, value = TRUE)

```

From the following code block, of the 173 majors, only 3 majors consist of "Data" or "Statistics".

## Question 2

The following code block will convert the following data:

`[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"`

`[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"`  

`[9] "elderberry"   "lime"         "lychee"       "mulberry"`    

`[13] "olive"        "salal berry"`

to

`c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe",`
`"chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")`

```{r echo=TRUE}

# Initialization

fruitsMain <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'

# Remove brackets and numbers
fruitsMod <- gsub('\\[\\d+\\]|\\s{2,}', '', fruitsMain)

# Splices at the quotes

fruitsModded <- unlist(strsplit(fruitsMod, '"')) 

# removes empty white spaces

fruitsModded <- trimws(fruitsModded[fruitsModded != "" & fruitsModded != " "])

fruitsModded <- paste0('c(', paste(shQuote(fruitsModded), collapse = ", "), ')')

#Print final product

cat(fruitsModded)

```

## Question 3

The following problems will be listed below to explain what will happen to each expression.

  a) `(.)\\1\\1`
  
```{r echo=TRUE}

alpha <- c("aaabcdef", "cheese", "banana", "wawawawaw", "Starlette", "Aurora", "Thalassa", "Apollo", "Bobobo", "haroldlorah")

str_view_all(alpha, "(.)\\1\\1", match=TRUE)

```
This highlights any character that is repeated three times.

  b) `"(.)(.)\\2\\1"`
  
```{r echo=TRUE}

str_view(alpha, "(.)(.)\\2\\1", match=TRUE)

```

This highlights any characters with xyyx.

  c) `(..)\\1`

```{r echo=TRUE}

str_view(alpha, "(..)\\1", match=TRUE)

```

This one highlights the characters with xyxy.

  d) `"(.).\\1.\\1"`
  
```{r echo=TRUE}

str_view(alpha, "(.).\\1.\\1", match=TRUE)

```
This looks for a single character that  repeats three times consecutively.

  e) `"(.)(.)(.).*\\3\\2\\1"`

```{r echo=TRUE}

str_view(alpha, "(.)(.)(.).*\\3\\2\\1", match=TRUE)

```
This is basically where the first three characters are followed by their reverse after some random text, this can also be names that are palindromic.

## Question 4

The following code blocks will answer the following questions below:
  
  a) Start and end with the same character. Answer: `^(.).*\\1$`

```{r echo=TRUE}

str_view(alpha, "^(.).*\\1$", match=TRUE)

```
  b) Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.) Answer: `(..).*\\1`
  
```{r echo=TRUE}

str_view(alpha, "(..).*\\1", match=TRUE)

```
  c) Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.) Answer: `(.).*\\1.*\\1`
  
```{r echo=TRUE}

str_view(alpha, "(.).*\\1.*\\1", match=TRUE)

```

